Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
Reviewing and accepting @fergunet 's taxonomy description

As these tools have several access levels, different detection methods or data control, there exist a number of aspects that the end-user needs to take into account to validate if a product fits his needs. Therefore, we propose the next taxonomy in order to classify the BYOD tools described in this paper.

\begin{itemize}
\item {\em Online or offline threat detection method}. Tools can identify security threats during runtime (online) or before their implantation (offline). For example, using some kind of Data Mining technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime. However, new rules can not be added. On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system follows an online scheme.
\item {\em Updatable of fixed information database}. This classification is related with the previous one. The new information gathered by the system during runtime can be stored in a database to generate new rules. If this database is not changed during runtime, as in the offline example explained above, the database is {\em fixed}. An example could be the hand-coded rules of a firewall, such as {\em iptables}, obtained from an offline method. On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable source for dynamic adaptation mechanisms. However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule are created. 
\item {\em Invasive or non-invasive data access}. A system can be considered {\em invasive} if a user needs to use the tool to perform his job. For example, open a specific browser provided by the tool, instead the original device browser, such as Chrome of Safari. A {\em non-invasive} data access is transparent to the user. An example is a log analyser daemon that updates other programs configuration or send information to the company server.
\item {\em Superuser or non-superuser system control}. Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices. However using superuser control may lead to a lack of privacy for the user.
\end{itemize}

>>>>

As these tools have several access levels, different detection methods, or diverse data control, there exist a number of aspects that the end-users need to take into account to validate if a product fits their needs. Therefore, we propose the next taxonomy in order to classify the BYOD tools described in this paper.

\begin{itemize}
\item {\em Online or offline threat detection method}. Tools can identify security threats during runtime (online) or before their implantation (offline). For example, using some kind of Data Mining technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime. However, new rules can not be added. On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system, follows an online scheme.
\item {\em Updatable of fixed information database}. This classification is related to the previous one. The new information gathered by the system during runtime can be stored in a database to generate new rules. If this database is not changed during runtime, as in the offline example explained above, the database is {\em fixed}. An example could be the hand-coded rules of a firewall, such as {\em iptables}, obtained from an offline method. On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable data source for dynamic adaptation mechanisms. However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule is created. 
\item {\em Invasive or non-invasive data access}. A system can be considered {\em invasive} if a user needs to use the tool to perform their job. For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari. Instead, a {\em non-invasive} data access is transparent to the user. An example is a log analyser daemon that updates other programs configuration or sends information to the company server.
\item {\em Superuser or non-superuser system control}. Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices. However using superuser control may lead to a lack of privacy for the user.
\end{itemize}
